\documentclass[10pt,a4paper]{article}

% --- Font & Layout Setup ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{helvet}         
\renewcommand{\familydefault}{\sfdefault}
\usepackage[margin=0.45in]{geometry} % Slightly tighter margins for more detail
\usepackage{setspace}       
\setstretch{1.25}            % Adjusted for high-density information

\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{tabularx}

% --- Stable 10.5pt Font Size Setup ---
\makeatletter
\renewcommand\normalsize{%
   \@setfontsize\normalsize{10.5pt}{12.5pt}%
   \abovedisplayskip 8\p@ \@plus2\p@ \@minus4\p@
   \belowdisplayskip \abovedisplayskip
   \let\@listi\@listI}
\normalsize
\makeatother

% --- Section Formatting ---
\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=0.15in, nosep, topsep=1pt, partopsep=0pt}

\begin{document}

% --- Header ---
\begin{center}
    {\Huge \textbf{HARSHA YAMAZALA}} \\
    \vspace{2pt}
    \textbf{Senior Platform Engineer $|$ CKA $|$ AWS Solutions Architect Pro} \\
    \vspace{2pt}
    \small 
    Reading, UK $|$ +44 7417433417 $|$ \href{mailto:hyamazala@gmail.com}{\faEnvelope \ hyamazala@gmail.com} \\
    \href{https://github.com/yamazalaharsha}{\faGithub \ github.com/yamazalaharsha} $|$ 
    \href{https://www.linkedin.com/in/harsha437/}{\faLinkedin \ linkedin.com/in/harsha437}
\end{center}

\section{Executive Summary}
Strategic Platform Engineering Leader with 10 years of experience architecting resilient, cloud-native Internal Developer Platforms (IDP) for Tier-1 financial institutions. Specialist in AKS and Azure DevOps, focusing on self-service ``Golden Path'' automation. Expert in embedding Zero-Trust networking and DevSecOps frameworks to meet strict regulatory standards while driving FinOps efficiency.

\section{Core Competencies}
\begin{itemize}[label=\textbullet, itemsep=1pt]
    \item \textbf{Networking \& Ingress:} Azure App Gateway (WAF v2), APIM, Istio Service Mesh, Atmos VPN, F5, Checkpoint.
    \item \textbf{Cloud Architecture:} Microsoft Azure (AKS, Landing Zones, Hub-Spoke), Entra ID, Workload Identities.
    \item \textbf{Infrastructure as Code:} Terraform (Modular Design), Azure Bicep, Ansible, Helm, GitOps.
    \item \textbf{Security \& Compliance:} Zero-Trust (mTLS), SAST/DAST, Aqua Security, Azure Policy, CyberArk.
    \item \textbf{Observability \& FinOps:} Dynatrace, Azure Monitor, KEDA (Scale-to-Zero), Kubecost, GreenOps.
\end{itemize}

\section{Professional Experience}

\textbf{LLOYDS BANKING GROUP} \hfill \textbf{2019 -- Present} \\
\textit{Platform (DevOps) Engineer} \hfill London, UK

\textit{Infrastructure Provisioning \& Pipeline Strategy}
\begin{itemize}
    \item Standardized provisioning via modular Terraform and GitOps, ensuring 80\% of Mortgages' Azure resources utilize repeatable ``Golden Path'' templates.
    \item Established secure state management using Azure Storage backends with mandatory locking, preventing configuration drift across multi-team deployments.
\end{itemize}

\textit{Security by Design \& Zero-Trust}
\begin{itemize}
    \item Engineered Zero-Trust environments using Istio mTLS and identity-first security through Microsoft Entra ID and Workload Identities.
    \item Embedded automated SAST/DAST and Aqua scanning into self-service pipelines, achieving 100\% regulatory compliance for mortgage applications.
\end{itemize}

\textit{Networking, Subnets \& Connectivity}
\begin{itemize}
    \item Designed scalable Hub-and-Spoke architectures with VNET peering and UDRs to isolate application tiers.
    \item Orchestrated network rules for Atmos VPN and F5 load balancers to enable secure, low-latency access for distributed teams.
    \item Collaborated with firewall teams on Checkpoint configurations to ensure 100\% adherence to bank-wide security policies.
\end{itemize}

\textit{Kubernetes (AKS) \& FinOps}
\begin{itemize}
    \item Orchestrated high-availability AKS clusters, driving 30\% waste reduction via KEDA scale-to-zero and rightsizing underutilized clusters.
    \item Integrated quality gates and full-stack observability (Dynatrace), reducing change failure rates to under 15\%.
\end{itemize}

\vspace{6pt}

\textbf{PEARSON INC} \hfill \textbf{Mar 2018 -- Feb 2019} \\
\textit{Senior Infrastructure Developer} \hfill Chennai, India
\begin{itemize}
    \item Migrated on-premise VMWare workloads to AWS and spearheaded SQL Server Always On Availability Groups.
    \item Executed global Docker containerization strategy ensuring portability and strict security baselines.
\end{itemize}

\vspace{6pt}

\textbf{CHARTER COMMUNICATIONS} \hfill \textbf{Jan 2016 -- Jan 2018} \\
\textit{DevOps Engineer} \hfill St. Louis, USA
\begin{itemize}
    \item Integrated Terraform with Puppet to automate telecommunications services in an OpenStack environment.
    \item Optimized server deployment strategies to maintain +99.9\% availability for customer-facing portals.
\end{itemize}

\section{Education}
\textbf{Master of Science in IT Management} \hfill New York, USA \\
Marist College

\end{document}